\subsection{Fast Diagonalization Method (FDM)}
    \BA{NEPTUNE interested in high-order methods- why?:
    \begin{itemize}
        \item  Better approximation properties (provided sufficient regularity- N.B. \emph{Not} necessarily the case with funky BCs in a tokamak, but \emph{should} be fine in my case if I pick a nice model with nice BCs on a nice domain).
        \item  Better numerical approximation properties. (Recall that diagram from the NEPTUNE workshop with the travelling bump).
        \item  Better suited to modern computer architectures. (Ask Pablo for more clarification here.)
    \end{itemize}
    Why not?:
    \begin{itemize}
        \item  Massively worse computational complexity- very dense matrices, unless we find some way to mitigate this...
    \end{itemize}}

    \BA{These equations require more orthogonality than traditional FDM can offer, right? Right. However, here's the big idea: Why do we need to stick to a polynomial basis?  \\
    What I mean by that is this: When working with FDM, we're working with tensors product finite elements, ultimately constructed from finite elements on the interval. For the complexes with which we're familiar, these interval FEs use function spaces of polynomials $\calP_{p}$. Standard FDM constructs $\sim p$ interior basis functions $(\phi_{i})$ for $\calP_{p}$ (or at least $\calP_{p}$ with appropriate $0$ BCs) as $\phi_{i} \in \calP_{p}$, such that we have agency over $\sim p^{2}$ coefficients for the basis. One ``set'' of orthogonality relations requires $\sim \frac{1}{2}p^{2}$ conditions on the basis coefficients. Working in this way therefore, standard FDM can only achieve 2 sets of orthogonality relations, usually:
    \begin{align}
        \langle\phi_{i}, \phi_{j}\rangle  =  \delta_{i, j}  &&
        \langle\phi_{i}', \phi_{j}'\rangle  =  \lambda_{i}\delta_{i, j}
    \end{align}
    Taking a step back, however, we can ask ourselves: \emph{``Why must we choose the function space on the interval element to be $\calP_{p}$?''}.  \\
    If, say, we were looking for $\sim p$ \emph{independent} functions $(\phi_{i})$ in $\calP_{\frac{3}{2}p}$, then we have agency over $\sim \frac{3}{2}p^{2}$ coefficients, and thus can choose over basis to satisfy 3 sets of orthogonality relations, say:
    \begin{align}
        \langle\phi_{i}, \phi_{j}\rangle  =  \delta_{i, j}  &&
        \langle\phi_{i}', \phi_{j}'\rangle  =  \lambda_{i}\delta_{i, j}  &&
        \langle\phi_{i}'', \phi_{j}''\rangle  =  \mu_{i}\delta_{i, j}
    \end{align}
    As such, we would be constructing our complex from a complex on the interval:
    \begin{center}\begin{tikzpicture}[align = center, node distance = 4cm, auto]
        \node (0) at (0, 0) {$\widetilde{P}_{p}^{0}  (<  \sim  P_{\frac{3}{2}p})$};
        \node (1) at (4, 0) {$\widetilde{P}_{p - 1}^{1}  (<  \sim P_{\frac{3}{2}p - 1})$};        
        \draw[->] (0) -- (1)
            node[midway, above] {$d$};
    \end{tikzpicture}\end{center}
    These are exactly the orthogonality relations we would need to apply FDM to Stokes.}

    \BA{What about if we construct each basis function iteratively instead? Twice the max polynomial degree, but can all be computed in advance and just read from a database.}
