\subsubsection*{Assumption 2: EM vs. Collisions Dominant Balance}
    Consider now the dominant terms in the Boltzmann equation (\ref{eqn:Boltzmann equation}) in a tokamak environment. Denote the scale of a variable, $*$, with an overbar, $\overline{*}$. Suppose the following scales are given by the problem specification:
    \begin{align}
        \left(\overline{n}_{s}\right)_{s},         &&
        \overline{\bfx},                           &&
        \overline{\bfv},                           &&
        \overline{\bfB},
    \end{align}
    where $n_{s}$ denote the particle density of species $s$,
    \begin{equation}
        n_{s}  :=  \int_{\bfv}f_{s}.
    \end{equation}

    \BA{Also: $(\rmq_{s})_{s}$, $(\rmm_{s})_{s}$.}
    
    The remaining variable scales are defined by:
    \begin{itemize}
        \item  $\overline{t}           :=  \overline{\bfx}/\overline{\bfv}$, working on convective timescales.
        \item  $\overline{\bfE}        :=  \overline{\bfv}\overline{\bfB}$, balancing the electric and magnetic Lorentz forces. \BA{(Why would this be the case?)}
        \item  $\overline{f}_{s}       :=  \overline{n}_{s}/\overline{\bfv}^{3}$, by the definition of $n_{s}$.
        \item  $\overline{\bfC}_{ss'}  :=  \max_{s}\{\overline{n}_{s}\}\overline{\bfB}/\max_{s'}\{\rmq_{s'}\}\overline{\bfv}^{2}$, by the requirement of a non-trivial dominant balance, here of the EM terms and collisional terms from phase $s'$ in phase $s$. \BA{(Further justification?)}
    \end{itemize}
    
    Terms in the Boltzmann equation (\ref{eqn:Boltzmann equation}) then have the scales:
    \begin{align}
        \overline{\partial_{t}f_{s} + \nabla_{\bfx}\cdot[f_{s}\bfv]}  &=  \frac{\overline{n}_{s}}{\overline{\bfx}\overline{\bfv}^{2}}  \label{eqn:convective scale}  \\
        \overline{\frac{\rmq_{s}}{\rmm_{s}}\nabla_{\bfv}\cdot[f_{s}(\bfE + \bfv\wedge\bfB)]}  &=  \frac{\rmq_{s}}{\rmm_{s}}\cdot\frac{\overline{n}_{s}\overline{\bfB}}{\overline{\bfv}^{3}}  \\
        \overline{\frac{\rmq_{s}\rmq_{s'}}{\rmm_{s}}\nabla_{\bfv}\cdot\bfC_{ss'}}  &=  \frac{\rmq_{s}\rmq_{s'}}{\rmm_{s}\max_{s}\{\rmq_{s'}\}}\cdot\frac{\max_{s}\{\overline{n}_{s}\}\overline{\bfB}}{\overline{\bfv}^{3}}  \label{eqn:collisional scale}
    \end{align}
    Regarding the values of these scales within a tokamak environment, consider the conditions during a typical JET reactor pulse, for a predominant (positive) deuterium ion (indexed via $*_{+}$) and (negative) electron (indexed via $*_{-}$) phase, with physical parameters for the JET reactor as listed in Chapters 2 and 4 of \cite{Wes00}:
    \begin{itemize}
        \item  $\overline{n}_{\pm}  \approx  10^{19}\rmm^{- 3}$.
        \item  $\overline{\bfx}     \approx  2.5\rmm$, twice the minor radius of $1.25\rmm$.
        \item  $\overline{\bfv}     \approx  7.9\ldots\times 10^{5}\rmm\rms^{- 1}$, the thermal velocity $\sqrt{\rmk_{\rmB}T/\rm\rmm_{+}}$ for the (mass/energy-dominant) ion phase at operational temperature $1.5\times 10^{8}\rmK$, in the middle of the range $1$--$2\times 10^{8}\rmK$.
        \item  $\overline{\bfB}     \approx  3.5\rmT$.
    \end{itemize}    
    The remaining scales then evaluate as:
    \begin{align*}
        \overline{t}           &\approx  3.2\times 10^{- 6}\rms              &
        \overline{\bfE}        &\approx  2.8\times 10^{6}\rmT\rmm\rms^{- 1}  \\
        \overline{f}_{\pm}     &\approx  2.1\times 10^{1}\rms^{3}\rmm^{- 6}  &
        \overline{\bfC}_{\pm_{1}\pm_{2}}  &\approx  3.5\times 10^{- 12}\rms^{3}\rmT^{2}{\rm kg}^{- 1}\rmm^{- 1}
    \end{align*}
    
    \begin{remark}[Justification for the non-relativistic model]
        Up until now, a non-relativistic model has been assumed. Observing that $\overline{\bfv}  \ll  c$, we see that this is in general a fair assumption, although relativistic effects are known to have some effects on tokamak plasma dynamics due to their impact on the very-high energy tails of the distribution functions.
    \end{remark}
    
    The scales (\ref{eqn:convective scale}--\ref{eqn:collisional scale}) for each phase thus evaluate, in $s^{2}\rmm^{- 6}$, as:
    \begin{align}
        \overline{\partial_{t}f_{\pm} + \nabla_{\bfx}\cdot[f_{\pm}\bfv]}  &\approx  6.5\ldots\times 10^{6}  \\
        \overline{\frac{\rmq_{+}}{\rmm_{+}}\nabla_{\bfv}\cdot[f_{+}(\bfE + \bfv\wedge\bfB)]}  =  \overline{\frac{\rmq_{+}q_{\pm}}{\rmm_{+}}\nabla_{\bfv}\cdot\bfC_{+\pm}}  &\approx  3.4\ldots\times 10^{9}  \\
        \overline{\frac{\rmq_{-}}{\rmm_{-}}\nabla_{\bfv}\cdot[f_{-}(\bfE + \bfv\wedge\bfB)]}  =  \overline{\frac{\rmq_{-}q_{\pm}}{\rmm_{-}}\nabla_{\bfv}\cdot\bfC_{-\pm}}  &\approx  1.3\ldots\times 10^{13}
    \end{align}
    Under tokamak conditions therefore, the Boltzmann equations for either phase are dominated by the EM terms, $\nabla_{\bfv}\cdot[f_{\pm}\left(\bfE + \bfv\wedge\bfB\right)]$, and the collisional terms $\nabla_{\bfv}\cdot\bfC_{\pm_{1}\pm_{2}}$, by a factor of approximately $7.5\ldots\times 10^{2}$ in the ion phase, and the stronger factor of approximately $1.4\ldots\times 10^{6}$ in the electron phase. \BA{(Check these numbers, they seem off when compared to the ratios for the dimensional values.)}

    \begin{remark}[Failure of EM vs. collision dominance in the Boltzmann equation for tokamak plasmas]
        While less than 1, these factors are comparitively large, due to the high temperatures and relatively short length scales in tokamak-like plasma environments, particularly for the ion phase on the order of $10^{3}$. Compare with the equivalent factor of around $10^{11}$ for the hydrogen phase in the full solar corona.

        It is primarily this factor that is responsible for the shortcoming of the fluid approximation for tokamak plasmas, and the high influence of kinetic effects on their dynamics.
    \end{remark}

    Assuming it holds true therefore that the EM and collisional terms achieve the dominant balance, the Boltzmann equations take the leading-order forms:
    \begin{align}\label{eqn:leading-order Boltzmann equation}
        \frac{\rmq_{s}}{\rmm_{s}}\nabla_{\bfv}\cdot[f_{s}(\bfE + \bfv\wedge\bfB)]  &\sim  \frac{\rmq_{s}}{\rmm_{s}}\sum_{s'}\rmq_{s'}\nabla_{\bfv}\cdot\bfC_{ss'}  \\
        \frac{\rmq_{s}}{\rmm_{s}}\nabla_{\bfv}\cdot\left[f_{s}(\bfE + \bfv\wedge\bfB) - \sum_{s'}\rmq_{s'}\bfC_{ss'}\right]  &\sim  0
    \end{align}
    