\subsection{Kinetic Models}
    \line

    \begin{definition}[Kinetic model]\label{def:kinetic model}
        Here, ``kinetic'' models refer to those wherein the distribution of particles positions and velocities is modelled through a single distribution function, as a function of both position and velocity.
    \end{definition}
    
    \line

    For each phase, $s$, define the distribution functions $(f_{s}(\bfx, \bfv; t))_{s}$ in the weak sense as
    \begin{equation}\label{eqn:distribution function definition}
        f_{s}(\bfx, \bfv; t)  :=  \sum_{i}\delta^{3}[\bfx - \bfx_{si}(t)]\delta^{3}[\bfv - \bfv_{si}(t)],
    \end{equation}
    where $\delta^{3}$ denotes the 3-dimensional (3D) $\delta$ function. While working with such $(f_{s})_{s}$ could \emph{in theory} be used to model all the particles exactly and simultaneously, variations in $\bfx$ of each $f_{s}$ occur on the length scale of the distances between particles, i.e. on the order of $10^{- 6}\rmm$ in a tokamak plasma. We would therefore need a mesh resolution on a similar (if not finer) length scale to capture the physical nature of each $f_{s}$. Again: computationally infeasible.

    For non-atomic scale simulations, such as those within a tokamak, the \emph{precise} position of each particle is generally irrelevant to the general fluid behavior when not working on the atomic scale. The key idea of kinetic theory is to model this distribution function as a \emph{random} distribution, as one might do in Bayesian statistics to model a parameter that is known to be of fixed value as a random variable when full information on it remains unknown. Due to the scale of the number of particles for tokamak-scale simulations, the impact this assumption has on the efficacy of the model is negligible. One defines the 1-particle distribution functions, denoted here as $\left(\widetilde{f_{s}}(\bfx, \bfv; t)\right)_{s}$, such that $\forall \phi(\bfx, \bfv; t)$,
    \begin{equation}
        \bbE\left\{\int_{\bfx, \bfv; t}f_{s}(\bfx, \bfv; t)\phi(\bfx, \bfv; t)\right\}
        \left(=  \sum_{i}\bbE\{\phi(\bfx_{si}, \bfv_{si}; t)\}\right)
        =  \int_{\bfx, \bfv; t}\widetilde{f_{s}}(\bfx, \bfv; t)\phi(\bfx, \bfv;t )
    \end{equation}
    Similarly the electromagnetic field must be modeled as a random distribution, with $\widetilde{\bfE}(\bfx, t)$, $\widetilde{\bfB}(\bfx, t)$ defined, such that $\forall \bfphi(\bfx, t)$,
    \begin{align}
        \bbE\left\{\int_{\bfx; t}\bfE(\bfx, t)\cdot\bfphi(\bfx, t)\right\}  =  \int_{\bfx; t}\widetilde{\bfE}(\bfx, t)\cdot\bfphi(\bfx, t)  \\ 
        \bbE\left\{\int_{\bfx; t}\bfB(\bfx, t)\cdot\bfphi(\bfx, t)\right\}  =  \int_{\bfx; t}\widetilde{\bfB}(\bfx, t)\cdot\bfphi(\bfx, t)
    \end{align}
    We seek to cast the exact equations in $(f_{s})_{s}$, $\bfE$, $\bfB$ into ones in the distribution parameters $(\widetilde{f_{s}})_{s}$, $\widetilde{\bfE}$, $\widetilde{\bfB}$. To do so, once can apply the workflow as outline in Figure \ref{fig:kinetic model construction workflow} to each equation.
    \begin{figure}[!ht]
        \centering
        \begin{tikzpicture}[align = center, auto]
            \node (1) at (0, 0) {Cast into variational form: $f_{s}  \mapsto  \int_{\bfx, \bfv; t}f_{s}\phi$};
            \node (2) at (1, -1.25) {Take expectations: $\int_{\bfx, \bfv; t}f_{s}\phi  \mapsto  \bbE\left\{\int_{\bfx, \bfv; t}f_{s}\phi\right\}$};
            \node (3) at (2, -2.5) {Convert to be in terms of distribution parameters: $\bbE\left\{\int_{\bfx, \bfv; t}f_{s}\phi\right\}  =  \int_{\bfx, \bfv; t}\widetilde{f_{s}}\phi$};
            \node (4) at (3, -3.75) {Cast back into strong form: $\int_{\bfx, \bfv; t}\widetilde{f_{s}}\phi  \mapsto  \widetilde{f_{s}}$};

            \draw[->] (1) -- (2);
            \draw[->] (2) -- (3);
            \draw[->] (3) -- (4);
        \end{tikzpicture}
        \caption{Diagram of workflow for construction of a kinetic model}
        \label{fig:kinetic model construction workflow}
    \end{figure}

    \shortline

    \paragraph*{Maxwell's Equations} Since this process is entirely linear, Maxwell's equations---themselves linear---carry over identically:
    \begin{align}
        \frac{1}{\rmc^{2}}\partial_{t}\widetilde{\bfE}  &=  \nabla\wedge\widetilde{\bfB} - \mu_{0}\sum_{s}\rmq_{s}\int_{\bfv}\widetilde{f_{s}}\bfv,  &
        \partial_{t}\widetilde{\bfB}  &=  - \nabla\wedge\widetilde{\bfE},  \\
        \frac{1}{\rmc^{2}}\nabla\cdot\widetilde{\bfE}  &=  \mu_{0}\sum_{s}\rmq_{s}\int_{\bfv}\widetilde{f_{s}},  &
        \nabla\cdot\widetilde{\bfB}  &=  0.
    \end{align}
    where:
    \begin{itemize}
        \item  $\rmc$ is the speed of light (in a vacuum), $\rmc  \approx  2.997\ldots\times 10^{8}\rmm\rms^{- 1}$.
        \item  $\mu_{0}$ is the vacuum permeability, $\mu{0}  \approx  1.257\ldots\times 10^{- 6}\rmT^{2}\rms^{2}\rmm^{1}{\rm kg}^{- 1}$.
    \end{itemize}
    \BA{I should probably initially define Maxwell's equations in the previous particle models subsection, instead of first here.}

    Defining the charge and current densities, $\rho_{\rmC}$ and $\bfj$ respectively, functions of $\bfx$ and $t$:
    \begin{align}
        \widetilde{\rho}_{\rmC}  :=  \int_{\bfv}\widetilde{f_{s}}\rmq_{s},  &&
               \widetilde{\bfj}  :=  \int_{\bfv}\widetilde{f_{s}}\rmq_{s}\bfv,
    \end{align}
    these can be written in the compact forms:
    \begin{align}
        \frac{1}{\rmc^{2}}\partial_{t}\widetilde{\bfE}  &=  \nabla\wedge\widetilde{\bfB} - \mu_{0}\widetilde{\bfj},  &
        \partial_{t}\widetilde{\bfB}  &=  - \nabla\wedge\widetilde{\bfE},  \label{eqn:Maxwell's equations transient}  \\
        \frac{1}{\rmc^{2}}\nabla\cdot\widetilde{\bfE}  &=  \mu_{0}\widetilde{\rho}_{\rmC},  &
        \nabla\cdot\widetilde{\bfB}  &=  0.  \label{eqn:Maxwell's equations steady-state}
    \end{align}
    
    \paragraph*{Boltzmann Equations} The evolution equations for $(f_{s})_{s}$ or $(\widetilde{f_{s}})_{s}$ are not as simple, due to their non-linearity. When applying this technique one derives the ``\emph{Boltzmann equations}'', \BA{[Ref]}
    \begin{equation}\label{eqn:Boltzmann equation}
        \partial_{t}\widetilde{f_{s}} + \nabla_{\bfx}\cdot\left[\widetilde{f_{s}}\bfv\right] + \frac{\rmq_{s}}{\rmm_{s}}\nabla_{\bfv}\cdot\left[\widetilde{f_{s}}\left(\widetilde{\bfE} + \bfv\wedge\widetilde{\bfB}\right)\right]  =   \frac{\rmq_{s}}{\rmm_{s}}\sum_{s'}\rmq_{s'}\nabla_{\bfv}\cdot\bfC_{ss'},
    \end{equation}
    where the collision terms $(\bfC_{ss'})_{ss'}$ are terms characterising the Coulomb collisions, defined as
    \begin{multline}\label{eqn:collision operator}
        \bfC_{ss'}\left[\widetilde{f_{s}}, \widetilde{f_{s'}}; \widetilde{f_{s}f_{s'}}\right](\bfx, \bfv; t)  :=  \int_{\bfx' \neq \bfx, \bfv'; t'}\left(\widetilde{f_{s}}(\bfx, \bfv; t)\widetilde{f_{s'}}(\bfx', \bfv'; t') - \widetilde{f_{s}f_{s'}}[(\bfx, \bfv; t), (\bfx', \bfv'; t')]\right)  \\
        [\bfk_{\bfE}(\bfx' - \bfx, \bfv'; t' - t) + \bfv\wedge\bfk_{\bfB}(\bfx' - \bfx, \bfv'; t' - t)],
    \end{multline}
    where in turn:
    \begin{itemize}
        \item  $\bfk_{\bfE}$, $\bfk_{\bfB}$, as functions in $\bfx'$, $\bfv'$, $t'$, are kernels of the electric and magnetic field, defined as the electric and magnetic fields produced at the origin by a unit point charge at position $\bfx'$ with velocity $\bfv'$ at time $t' \left(\in \left[-\frac{1}{c}\|\bfx'\|, 0\right]\right)$. \BA{(Explicit definition for $\bfk_{\bfE}$, $\bfk_{\bfB}$? Not really needed for the theory.)}
        
        \item  The 2-particle distributions functions $\left(\widetilde{f_{s_{1}}f_{s_{2}}}[(\bfx_{1}, \bfv_{1}; t_{1}), (\bfx_{2}, \bfv_{2}; t_{s})]\right)_{s_{1}s_{2}}$ are defined such that $\forall \phi[(\bfx_{1}, \bfv_{1}; t_{1}), (\bfx_{2}, \bfv_{2}; t_{2})]$,
        \begin{multline}
            \bbE\left\{\int_{\bfx_{1}, \bfv_{1}; t_{1}}\int_{\bfx_{2}, \bfv_{2}; t_{2}}f_{s_{1}}(\bfx_{1}, \bfv_{1}; t_{1})f_{s_{2}}(\bfx_{2}, \bfv_{2}; t_{2})\phi[(\bfx_{1}, \bfv_{1}; t_{1}), (\bfx_{2}, \bfv_{2}; t_{2})]\right\}  \\
            \left(=  \sum_{i_{1}, i_{2}}\bbE\{\phi[(\bfx_{s_{1}i_{1}}, \bfv_{s_{1}i_{1}}; t_{1}), (\bfx_{s_{2}i_{2}}, \bfv_{s_{2}i_{2}}; t_{2})]\}\right)  \\
            =  \int_{\bfx_{1}, \bfv_{1}}\int_{\bfx_{2}, \bfv_{2}}\widetilde{f_{s_{1}}f_{s_{2}}}[(\bfx_{1}, \bfv_{1}; t_{1}), (\bfx_{2}, \bfv_{2}; t_{2})]\phi[(\bfx_{1}, \bfv_{1}; t_{1}), (\bfx_{2}, \bfv_{2}; t_{2})].
        \end{multline}
        These capture some of the nature of how the positions of pairs of particles are correlated.
    \end{itemize}
    For a full derivation of (\ref{eqn:Boltzmann equation}) see Appendix \ref{cha:Boltzmann equation derivation}.

    Obviously this system is not closed, as it in turn is dependent on $\left(\widetilde{f_{s_{1}}f_{s_{2}}}\right)_{s_{1}s_{2}}$; this is referred to as the ``\emph{closure problem}''. Different approximations to $\left(\widetilde{f_{s_{1}}f_{s_{2}}}\right)_{s_{1}s_{2}}$ lead to different collisional forces and collision operators in the Boltzmann equation.

    \shortline

    From here, we shall drop the tildes $\widetilde{*}$ on $\widetilde{f_{s}}$, $\widetilde{\bfE}$, $\widetilde{\bfB}$, $\widetilde{\rho}_{\rmC}$, $\widetilde{\bfj}$, as we shall not be returning to the particle model. Together this system can be refered to as the Boltzmann--Maxwell system.

    \line
    
    \begin{lemma}[Momentum and energy conservation on $(\bfC_{ss'})_{ss'}$]\label{lem:conservation on collision operators}
        The following two identities hold on $(\bfC_{ss'})_{ss'}$:
        \begin{align}
            \int_{\bfx}\left[\sum_{s, s'}\rmq_{s}\rmq_{s'}\int_{\bfv}\bfC_{ss'}\right]           =  \bfzero,  &&
            \int_{\bfx}\left[\sum_{s, s'}\rmq_{s}\rmq_{s'}\int_{\bfv}\bfC_{ss'}\cdot\bfv\right]  =  0.
        \end{align}
    \end{lemma}
    \begin{proof}
        By the conservation of momentum and energy over the whole domain:
        \begin{align}
            \partial_{t}\left[\sum_{s}\int_{\bfx, \bfv}f_{s}\rmm_{s}\bfv\right]                     &=  \sum_{s}\int_{\bfx}\left[f_{s}\rmq_{s}(\bfE + \bfv\wedge\bfB)\tall\right]  \\
            \partial_{t}\left[\sum_{s}\int_{\bfx, \bfv}f_{s}\frac{1}{2}\rmm_{s}\|\bfv\|^{2}\right]  &=  \sum_{s}\int_{\bfx}\left[f_{s}\rmq_{s}(\bfE + \bfv\wedge\bfB)\cdot\bfv\tall\right]
        \end{align}
        Substituting the Boltzmann equation (\ref{eqn:Boltzmann equation}) for $\partial_{t}f_{s}$, the given results follow.

        \BA{Does this need some appropriate decay condition on $(f_{s})_{s}$ so that I can apply integration by parts that I've forgotten to mention? In fact, the same is true later for the collision operators $(\bfC_{ss'})_{ss'}$ when I'm deriving the fluid model too, I should go through and check what decay conditions need mentioning.}
    \end{proof}
    
    \begin{remark}
        By the same logic for the conservation of mass,
        \begin{equation}
            \partial_{t}\left[\sum_{s}\int_{\bfx, \bfv}f_{s}\rmm_{s}\right]  =  0,
        \end{equation}
        however this result holds necessarily for all $(\bfC_{ss'})_{ss'}$.
    \end{remark}

    \line


    \input{0 - introduction/2 - plasma modeling/2 - kinetic models/1 - non-dimensionalization/main.tex}
    