\chapter{Physical Model and System of Equations}
    \BA{Introduction.}
    
    \BA{Room for lots of pictures here.}
    
    \BA{What physics characterise a (magnetised) neutral plasma? Quasi-neutral mix of \emph{separated} electrically-charged phases. (Check out the \href{https://en.wikipedia.org/wiki/Plasma_(physics)}{plasma Wikipedia page}.)}
    
    \BA{Creates a coupled system with the EM field.}
    
    \BA{What causes a fluid to turn into a plasma? Ionisation. (High heat/strong EM field.)}
    
    \BA{What makes a tozmahok plasma special (give stats):
    \begin{itemize}
        \item  \emph{Massive} heat.
        \item  \emph{Massive} magnetic field- highly magnetised. (Talk about particle gyro-orbits and drifts.)
        \item  \emph{Minimal} density. (Why?)
    \end{itemize}.}
    
    \BA{Will make the assumptions:
    \begin{itemize}
        \item  Only 2 phases- this is generally the case in edge plasmas (i.e. outside the divertor) provided impurity effects are negligible. (A bold assumption?)
        \item  Only (thermalising) Coulomb collisions are considered- these are generally dominant over the others in a tozmahok. (N.B. No fusion.)
        \item  Relativistic effects are negligible. (Is observing that the velocity scale is much smaller than $c$ sufficient justification? Imperial guy at the NEPTUNE workshop appeared to think not.)
    \end{itemize}}
    
    \BA{Complicated BCs in a tozmahok.}
    
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}[align = center, node distance = 4cm, auto]
            \node[1] (11) at (0, 0) {{\bf Fluid} Single-Phase Model (Navier–Stokes)};
            \node[2] (12) at (0, -1.75) {{\bf Kinetic} Single-Phase Model};
            \node[2] (21) at (5.5, 0) {{\bf Fluid} Multi-phase Model};
            \node[3] (22) at (5.5, -1.75) {{\bf Kinetic} Multi-phase model};
            \node[3] (31) at (11, 0) {{\bf Fluid} Plasma Model (MHD)};
            \node[4] (32) at (11, -1.75) {{\bf Kinetic} \\ Plasma Model};
    
            \path[arrow] (11) -- (12);
            \path[arrow] (11) -- (21);
            \path[arrow] (12) -- (22);
            \path[arrow] (21) -- (22);
            \path[arrow] (21) -- (31);
            \path[arrow] (22) -- (32);
            \path[arrow] (31) -- (32);
        \end{tikzpicture}
        \caption{\BA{Diagram of workflow for creating a kinetic plasma model to account for pressure anisotropy.}}
    \end{figure}
    
    
    \section{Kinetic Models}
        \BA{What is a ``kinetic'' model.}
        
        \subsection{Single-Phase Fluids}
            \BA{The resultant kinetic PDE. (Boltzmann equation.)}
                        
            \BA{How we traditionally convert that to a ``fluid'' model.}
            
            \BA{Will use this simpler case as a reference study to develop the ideas for the more complicated tozmahok plasma case.}

        \subsection{Multiphase Fluids}
            \BA{Similar analysis for a multiphase fluid, in preparation for handling the tozmahok plasmas.}
        
        \subsection{Tozmahok Plasmas}
            \BA{Why the fluid/MHD model reductions aren't necessarily valid in tozmahok plasmas. (Incorrectly assumed dominant collisional term- get some estimates on the scale of these terms in the edge plasma. Good content under ``Mathematical Descriptions'' \href{https://en.wikipedia.org/wiki/Plasma_(physics)}{here}.)}
            
            \BA{Many effects not captured my MHD/2 fluid models (check out \href{https://upload.wikimedia.org/wikipedia/commons/a/a9/A_Comparison_Chart_For_Modeling_Plasma2.png}{this} diagram off Wikipedia, or again the content under ``Mathematical Descriptions'' \href{https://en.wikipedia.org/wiki/Plasma_(physics)}{here}.):
            \begin{itemize}
                \item  Most plasma waves
                \item  Most plasma/kinetic instabilities
                \item  Landau damping/bump-on-tail instability
                \item  Leakage
                \item  Structures (Beams/Double layers)
                \item  Anisotropic pressure
            \end{itemize}}
            
            \BA{The resultant kinetic PDE. (Boltzmann/Vlasov equations.)}
            
            \BA{Talk about gyrokinetic model:
            \begin{itemize}
                \item  The model's physical basis/mathematics. (Equations provide good insight into the origin of some behavioural effects, e.g. gyro-orbits/drifts.)
                \item  Why we don't use it on the general kinetic equation:
                \begin{itemize}
                    \item  High mathematical (more terms in lower dimensions doesn't necessarily mean faster computation)/computational (really don't want to do a 5D simulation) complexity.
                    \item  Errors from neglection of terms. (Non-physical behaviour over long times/resonances and adiabatic invariants can be lost.)
                \end{itemize}
                \item  We \emph{will} however use it for the PIC correction.
            \end{itemize}}
    
    
    \section{Coupled Maxwellian/Correction Decomposition}
        \BA{How we can re-adapt the techniques that traditionally give a fluid model when the collision operator is non-dominant to get an accurate fluid model, to apply modern techniques in fluid simulation?}
        
        \BA{Expand as a sum of a Maxwellian and some correction!}
        
        \subsection{Maxwellian Background: A \emph{Fluid} Model}
            \BA{Ideas already well-developed!}
            
            \BA{Correction contribution not too problematic (hopefully).}
            
        \subsection{Anisotropic Correction: A \emph{Kinetic} Model}
            \BA{Not just kicking the problem down the road- plasma is thermalised/Maxwellian in ``most places'' for ``most physically relevant simulations'', so the correction is (compartively) small in ``most places''.}
            
            \BA{How do we model this:
            \begin{itemize}
                \item  Lattice Boltzmann?
                \item  Some series expansion?
                \item  Particle-in-cell (PIC)?
            \end{itemize}}
    
    
    \section{Edge Plasma Model}
        \BA{Little about the edge plasma model we're going to consider:
        \begin{itemize}
            \item  Looking for symmetric structures on a low aspect ratio?
            \item  Idk there's a lot of ways to consider this- I could very well end up doing different kinds of simulations with all different kinds of BCs in the final product, and seeing how my results match up.
        \end{itemize}}

    \section*{Summary}
        \BA{Summary.}