\subsection{Functions Spaces/Finite Elements in Time (FET)}\label{cha:FET}
    As an alternative approach, one can interpret (\ref{eqn:general time-dependent PDE}) on the space-\emph{time} domain $\bfOmega\otimes T$, where $T$ represents a time interval: potentially the timestep $\left(t^{n}, t^{n + 1}\right]$, potentially the whole simulation interval $\left(0, t^{N}\right]$. One then casts into a weak form by testing directly against test functions defined similarly over the whole space-time domain $\bfOmega\otimes T$.
    
    FET transfers the traditional independent choice of RK method to one of a choice of the behavior of the function spaces and Galerkin discretizations in time, in their continuity, order, etc.
    
    A few key points on this technique:
    \begin{itemize}
        \item  For tensor product domains, $\bfOmega\otimes T$, such spaces can often be constructed via the tensor product of spaces on $d$-dimensional $\bfOmega$ and 1-dimensional $T$, without needing to construct new spaces on the entire $(d + 1)$-dimensional domain $\bfOmega\otimes T$.
        \item  The test function spaces need not be identical to the trial function spaces (i.e. a \emph{Petrov}--Galerkin methods) and often won't be for systems with an odd order in time.
        \item  When using a FET interpretation, the intention is often \emph{not} to solve a highly computationally intense, $(d + 1)$-dimensional FE problem on all of $\bfOmega\otimes T$, but to extract a timestepper from the discretization that need only be solved on the $d$-dimensional spatial domain, $\bfOmega$, by exploiting block-triangularity in the stiffness \BA{(Is this the right terminology here?)} matrix. Such block-triangular matrix are derived from well-posed weak forms where the test space has no strongly-imposed initial conditions, such as $*\otimes H^{1}_{+}(T)$ or $*\otimes L^{2}(T)$. \BA{(Check.)} For linear problems, it is in fact often the case that the resultant timesteppers are identical to certain ones that would be derived from a RK-scheme interpretation.
    \end{itemize}
    There are many benefits to a FET interpretation that are often lacking in traditional RK techniques:
    \begin{itemize}
        \item  Crucially, FET provides a weak formulation that often perfectly aligns with the kind of results needed to prove structure-preserving properties.
        \item  FET interpretations inherit much of the useful results and techniques of traditional spatial FEM, including:
        \begin{itemize}
            \item  Finite-element exterior calculus (FEEC).
            \item  Multigrid (at least for non-Petrov--Galerkin schemes).
            \item  Well-studied interpolation and projection error estimates.
            \item  Language for the analysis and interpretation of non-confoming schemes.
            \item  Agency over bases for the time discretization with good orthogonality properties. \BA{(FDM- I want to make a remark on this later.)}
            \item  Easy extension to high order
        \end{itemize}
        \item  Solutions provided by FET are meaningful at all times. \BA{(This is important for me.)}
        \item  FET is the perfect language for solving problems that are already posed on a space-time domain, such as:
        \begin{itemize}
            \item  Searching for periodic solutions. \BA{(I need to do a good note about this somewhere- about how we solve for time periods for periodic problems, since this is something I really want to consider.)}
            \item  Problems with moving boundaries, where the space-time domain can \emph{not} be written in the tensor-product form $\bfOmega\otimes T$.
        \end{itemize}
    \end{itemize}
    
    \BA{Should go through and add correct punctuation to my equations.}
    

    \input{3 - fluid component/2 - structure preservation/2 - FET/1 - heat equation/main.tex}
    \input{3 - fluid component/2 - structure preservation/2 - FET/2 - construction/main.tex}
    \input{3 - fluid component/2 - structure preservation/2 - FET/3 - heat equation (revisited)/main.tex}
    \input{3 - fluid component/2 - structure preservation/2 - FET/4 - Hamiltonian systems/main.tex}
    \input{3 - fluid component/2 - structure preservation/2 - FET/5 - Navier--Stokes/main.tex}
    