\subsection{Functions Spaces/Finite Elements in Time (FET)}\label{cha:FET}
    One can alternatively interpret (\ref{eqn:general time-dependent PDE}) directly over the full space-\emph{time} domain $\bfOmega\otimes T^{n}$. This is interpreted as a domain in the classical spatial sense, with $\bfOmega\otimes T^{n}  \subset  \bbR^{d + 1}$ when $\bfOmega  \subset  \bbR^{d}$. One can discretize the system over this domain using whatever classical technique is desired. In our case this is the finite-element method, or, since the domain is in space-\emph{time}, finite elements in time (FET). The value taken by $\bfu$ at the start of the interval, $\bfu^{n}$, can be interpreted as one BC, with the value taken by $\bfu$ at the \emph{end} of the interval, $\bfu^{n + 1}$, following the definition of the restriction of the solution to the final time, $\bfu^{n + 1}  =  \bfu|_{t^{n + 1}}$.
    
    When using FET, the traditional independent choice of RK method when constructing a timestepper is transferred to one of the behavior of the function spaces and Galerkin discretizations in time, in their continuity, order, etc.
    
    A few key points on FET timesteppers:
    \begin{itemize}
        \item  Due to the tensor product nature of the space-time domain, $\bfOmega\otimes T^{n}$, the space-time trial and test function spaces in variational formulations can often be constructed via the tensor product of spaces on the spatial, $\bfOmega$, and time, $T^{n}$, domains without needing to construct new spaces on the entire space-time domain, $\bfOmega\otimes T^{n}$.
        \item  The test function spaces need not be identical to the trial function spaces (i.e. a \emph{Petrov}--Galerkin methods) and often won't be. This is natural with the odd order in time.
        \item  The intention of this approach is typically \emph{not} to solve an even higher dimension FE problem on all of $\bfOmega\otimes T^{n}$, but to pick discrete trial and test spaces in the Galerkin variational formulation that have a fixed, small number of DoFs in time---$\calO[s]$ in the sense of the number of steps of an RK method---such as $*\left(\bfOmega^{\rmh}\right)\otimes\bbP_{s}\left(T^{n}\right)$ or $*\left(\bfOmega^{\rmh}\right)\otimes\bbDP_{s - 1}\left(T^{n}\right)$.
    \end{itemize}
    FET interpretations provide certain benefits over traditional RK techniques:
    \begin{itemize}
        \item  Crucially, FET often provides variational formulations that align with those needed to prove structure-preserving properties directly.
        \item  FET interpretations inherit much of the useful results and techniques of traditional spatial FEM, including:
        \begin{itemize}
            \item  Finite-element exterior calculus (FEEC).
            \item  Parallel-in-time methods.
            \item  Well-studied interpolation and projection error estimates.
            \item  Language for the analysis and interpretation of non-confoming schemes.
            \item  Agency over bases for the time discretization with good orthogonality properties.
            \item  Easy extension to high order.
        \end{itemize}
        \item  Solutions provided by FET are meaningful at all times. As noted in Section \ref{cha:FEM vs. PiC} this will be particularly useful in our case when interacting with the kinetic correction in the future. 
        \item  FET can be the perfect language for solving problems that are already posed on a space-time domain, such as:
        \begin{itemize}
            \item  Searching for periodic solutions.
            \item  Problems with moving boundaries, where the space-time domain can \emph{not} be written in the tensor-product form $\bfOmega\otimes T^{n}$.
        \end{itemize}
    \end{itemize}
    

    \input{2 - fluid component/2 - structure preservation/2 - FET/1 - heat equation/main.tex}
    \input{2 - fluid component/2 - structure preservation/2 - FET/2 - construction/main.tex}
    \input{2 - fluid component/2 - structure preservation/2 - FET/3 - heat equation (revisited)/main.tex}
    \input{2 - fluid component/2 - structure preservation/2 - FET/4 - Hamiltonian systems/main.tex}
    \input{2 - fluid component/2 - structure preservation/2 - FET/5 - Navier--Stokes/main.tex}
    