\section{Kinetic Models}
    \BA{What is a ``kinetic'' model?}
    
    \begin{definition}[Kinetic model]
        Here, ``kinetic'' model refers to a model wherein a fluid is modelled via a particle density function of position and velocity (and time).
    \end{definition}
    
    This is typically written as $f(\bfx, \bfv; t)$. Obviously, with the high dimensionality, this can be computationally prohibitive, so we'd like to avoid such a model if possible.
    
    \BA{Boltzmann equation definition here.}
    
    \begin{definition}[Fluid model]
        Here, ``fluid'' model refers to a reduced kinetic model, where a collection of functions of position (and time) only are modelled.
    \end{definition}
    
    These typically define certain properties of the kinetic model density function, $f$, at each position, $\bfx$, to in some way capture the physics of the full kinetic model. The Navier–Stokes equations, for example, can be found from the assumption that collisions between particles dominate the behaviour of each particle, such that at each position, $\bfx$, the kinetic model density function, $f|_{\bfx}$, converges to a high entropy state (often a scaled normal distribution: a Maxwellian) characterised by 3 conserved variables:
    \begin{itemize}
        \item  Mass (per unit volume, i.e. density)
        \item  Momentum (per unit volume)
        \item  Energy (per unit volume, i.e. temperature after conservation of mass of momentum)
    \end{itemize}
    When collisions between particles do \emph{not} dominate the particle behaviour—as is the case in the very low density, high temperature \BA{(Does this increase or decrease the size of the Coulomb collision term?)} tozmahok plasmas—the assumptions that give rise to these fluid approximations often break down, implying that, without modification, these models fail to capture so-called ``kinetic effects'' \BA{(Such as?)}.
    
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}[align = center, node distance = 4cm, auto]
            \node[1] (11) at (0, 0) {{\bf Fluid} Single-Phase Model (Navier–Stokes)};
            \node[2] (12) at (0, -1.75) {{\bf Kinetic} Single-Phase Model};
            \node[2] (21) at (5.5, 0) {{\bf Fluid} Multi-phase Model};
            \node[3] (22) at (5.5, -1.75) {{\bf Kinetic} Multi-phase model};
            \node[3] (31) at (11, 0) {{\bf Fluid} Plasma Model (MHD)};
            \node[4] (32) at (11, -1.75) {{\bf Kinetic} \\ Plasma Model};
    
            \path[arrow] (11) -- (12);
            \path[arrow] (11) -- (21);
            \path[arrow] (12) -- (22);
            \path[arrow] (21) -- (22);
            \path[arrow] (21) -- (31);
            \path[arrow] (22) -- (32);
            \path[arrow] (31) -- (32);
        \end{tikzpicture}
        \caption{\BA{Diagram of workflow for creating a kinetic plasma model to account for pressure anisotropy.}}
    \end{figure}
    
    \subsection{Single-Phase Fluids}
        \BA{The resultant kinetic PDE. (Boltzmann equation.)}
                    
        \BA{How we traditionally convert that to a ``fluid'' model.}
        
        \BA{Will use this simpler case as a reference study to develop the ideas for the more complicated tozmahok plasma case.}
        
        \BA{The way I've got this section structured with reference to introducing the moments is a bit funny.}
        
        Consider first a single-phase fluid. Let a single particle of mass $m$ in this fluid have position $\bfx(t)$ and velocity $\bfv(t)$, and be subject to a force $\bfF(\bfx, \bfv; t)$. We seek a (system of) ODEs governing the behaviour of this particle:
        \begin{itemize}
            \item  The position evolves simply according to the ODE
            \begin{equation}\label{velocity ODE}
                d\bfx  =  \bfv dt
            \end{equation}
            \item  The velocity evolves according to the ODE, $d\bfv  =  \frac{1}{m}\bfF dt + \frac{1}{m}${\bf ``Collisional forces''}$dt$. \BA{(Note here with references about how tough it is to model collisional terms- \emph{got} to make \emph{some} assumptions, \emph{especially} if we want to do simulations!)} To model the collisional forces, consider the following 2 assumptions:
            \begin{itemize}
                \item  The molecular chaos hypothesis:
                \begin{definition}[Molecular chaos hypothesis]
                    The ``molecular chaos hypothesis'' postulates that the velocities of colliding particles are uncorrelated, and independent of position. \BA{[Ref]} \BA{(Justification that this is valid here? Particle number sufficiently large?)}
                \end{definition}
                \item  Collisional forces on the particles are dominated by those from Coulomb collisions: \BA{(Is this the right way of phrasing this?)}
                \begin{definition}[Coulomb collision]
                    A ``Coulomb collision'' is an elastic collision between two charged particles interacting through their own electric field. \BA{[Ref]} \BA{(Justification that this is valid here?)}
                \end{definition}
            \end{itemize}
            We can then model the collision forces through a Wiener process, with forces proportional to the:  \BA{(Give justification for this model. That might be tough...)}
            \begin{itemize}
                \item  Difference in momentum between that of the particle, $m\bfv$, and the average particle at that position's space, $m\bfu$ \BA{(Why?)}
                \begin{equation}
                    \mu m(\bfu - \bfv)
                \end{equation}
                \item  Derivative of some Wiener process, representing the random forces from collisions at random angles from the molecular chaos hypothesis
                \begin{equation}
                    \sigma\frac{d\bfB}{dt}
                \end{equation}
            \end{itemize}
            
            \BA{Here's where I think I should state that we have the relation $\frac{\mu}{\sigma^{2}}  =  \frac{k_{B}T}{m}$. Is this from conservation of energy? Would like to give a proper derivation of the scale of $\sigma$, and am sure I'll have to for the dimensional analysis.}
            
            By convention, mapping $\bfx, \bfv  \mapsto  \bfX, \bfV$ to represent the switch from an ODE to an SDE (and accordingly in (\ref{velocity ODE})) gives the SDE for the velocity evolution
            \begin{equation}
                \item  d\bfV  =  \frac{1}{m}\bfF dt + \mu m(\bfu - \bfv)dt + \sigma d\bfB
            \end{equation}
            This resembles a combination of an Ornstein–Uhlenbeck process and a forcing term.
        \end{itemize}
        Applying the Fokker-Planck equation, the particle density function, $f(\bfx, \bfv; t)$ evolves according to the PDE
        \begin{equation}
            \partial_{t}[f] + \nabla_{\bfx}\cdot[f\bfv] + \frac{1}{m}\nabla_{\bfv}\cdot[f\bfF]  =  \underset{\textrm{Collisional terms}}{\underbrace{\mu\nabla_{\bfv}\cdot[f(\bfv - \bfu)] + \frac{\sigma^{2}}{2}\Delta_{\bfv}[f]}}
        \end{equation}
        This is a form of the Boltzmann equation, where the approximation to the collisional term is explicitly derived from the above assumptions.
        
        \BA{Think what I've got written going forwards here should be in the \emph{next} subsection.}
        
        It is often the case that on the typical parameter scales of interest, collisional terms massively dominate the above PDE. \BA{(Dimensional analysis here?)} As such, up to leading order we would expect
        \begin{align}
            0  &\sim  \mu\nabla_{\bfv}\cdot[f(\bfv - \bfu)] + \frac{\sigma^{2}}{2}\Delta_{\bfv}[f]  \\
            f  &\sim  \frac{\rho}{m}\sqrt{\frac{m}{k_{B}T}}^{3}\exp\left(- \frac{m}{2k_{B}T}\|\bfv - \bfu\|^{2}\right)  \\
        \end{align}
        where $\rho$, $\bfu$, $T$—functions of $\bfx$ (and $t$)—are moments characterising the conserved quantities of mass, momentum and energy:
        \begin{align}
            \rho  &=  \int fmd\bfv  \\
            \rho\bfu  &=  \int fm\bfvd\bfv d\bfv  \\
            \frac{1}{2}\rho\left(\|\bfu\|^{2} + 3\frac{k_{B}T}{m}\right)  &=  \int f\frac{1}{2}m\|\bfv\|^{2}d\bfv  \\
        \end{align}
        \BA{(Is my energy equation right there? I think so, have checked a little, plus the dimensions seem right.)} and, by its definition from the energy equation here, \BA{(Don't like the way that's phrased...)} $k_{B}  \approx  1.381\times10^{- 23}\rmJ\rmK^{- 1}$ is the Boltzmann constant.
    
    \subsection{Multiphase Fluids}
        \BA{Similar analysis for a multiphase fluid, in preparation for handling the tozmahok plasmas.}
    
    \subsection{Tozmahok Plasmas}
        \BA{Why the fluid/MHD model reductions aren't necessarily valid in tozmahok plasmas. (Incorrectly assumed dominant collisional term- get some estimates on the scale of these terms in the edge plasma. Good content under ``Mathematical Descriptions'' \href{https://en.wikipedia.org/wiki/Plasma_(physics)}{here}.)}
        
        \BA{Many effects not captured my MHD/2 fluid models (check out \href{https://upload.wikimedia.org/wikipedia/commons/a/a9/A_Comparison_Chart_For_Modeling_Plasma2.png}{this} diagram off Wikipedia, or again the content under ``Mathematical Descriptions'' \href{https://en.wikipedia.org/wiki/Plasma_(physics)}{here}.):
        \begin{itemize}
            \item  Most plasma waves
            \item  Most plasma/kinetic instabilities
            \item  Landau damping/bump-on-tail instability
            \item  Leakage
            \item  Structures (Beams/Double layers)
            \item  Anisotropic pressure
        \end{itemize}}
        
        \BA{The resultant kinetic PDE. (Boltzmann/Vlasov equations.)}
        
        \BA{Talk about gyrokinetic model:
        \begin{itemize}
            \item  The model's physical basis/mathematics. (Equations provide good insight into the origin of some behavioural effects, e.g. gyro-orbits/drifts.)
            \item  Why we don't use it on the general kinetic equation:
            \begin{itemize}
                \item  High mathematical (more terms in lower dimensions doesn't necessarily mean faster computation)/computational (really don't want to do a 5D simulation) complexity.
                \item  Errors from neglection of terms. (Non-physical behaviour over long times/resonances and adiabatic invariants can be lost.)
            \end{itemize}
            \item  We \emph{will} however use it for the PIC correction.
        \end{itemize}}